A Bayesian Perspective \\\large{Extracorporeal CPR for Refractory Out-of-Hospital Cardiac Arrest}

### 2023-02-12 manuscript/manuscript.qmd
minor touch ups

The "take home" message from this study is that standard statistical analyses resulting in a conclusion of "similar survival effects" may be overly simplified and potentially inaccurate. This Bayesian analysis demonstrates that while any definitive conclusions regarding the superiority, inferiority or equivalence of eCPR to cCPR are lacking. Rather the possibility of a clinically meaningful benefit, or even less likely the possibility of clinically meaningful harm, has not been reasonably excluded and continued research is necessary to clarifying the remaining uncertainties. The final dilemma confronting clinicians is that even Bayesian analyses of randomized trials provide only probability estimates for an average treatment effect and not for the elusive individual treatment effect.

>>>>

The "take home" message from this study is that standard statistical analyses resulting in a conclusion of "similar survival effects" may be overly simplified and potentially inaccurate. This Bayesian analysis demonstrates that any definitive conclusions regarding the superiority, inferiority, or equivalence of eCPR to cCPR are lacking. Rather the possibility of a clinically meaningful benefit, or less likely the possibility of clinically meaningful harm, has not been reasonably excluded and continued research is necessary to clarifying the remaining uncertainties. The final dilemma confronting clinicians is that even Bayesian analyses of randomized trials provide only probability estimates for *average* treatment effect and not for the elusive *individual* treatment effect.

### 2023-02-12 manuscript/manuscript.tex
minor touch ups

\begin{keyword}
    extracorporeal CPR \sep 
    Bayesian statistics
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

The ``take home'' message from this study is that standard statistical
analyses resulting in a conclusion of ``similar survival effects'' may
be overly simplified and potentially inaccurate. This Bayesian analysis
demonstrates that while any definitive conclusions regarding the
superiority, inferiority or equivalence of eCPR to cCPR are lacking.
Rather the possibility of a clinically meaningful benefit, or even less
likely the possibility of clinically meaningful harm, has not been
reasonably excluded and continued research is necessary to clarifying
the remaining uncertainties. The final dilemma confronting clinicians is
that even Bayesian analyses of randomized trials provide only
probability estimates for an average treatment effect and not for the
elusive individual treatment effect.

>>>>

\begin{keyword}
    extracorporeal CPR \sep 
    Bayesian statistics
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, enhanced, interior hidden]}{\end{tcolorbox}}\fi

@@

The ``take home'' message from this study is that standard statistical
analyses resulting in a conclusion of ``similar survival effects'' may
be overly simplified and potentially inaccurate. This Bayesian analysis
demonstrates that any definitive conclusions regarding the superiority,
inferiority, or equivalence of eCPR to cCPR are lacking. Rather the
possibility of a clinically meaningful benefit, or less likely the
possibility of clinically meaningful harm, has not been reasonably
excluded and continued research is necessary to clarifying the remaining
uncertainties. The final dilemma confronting clinicians is that even
Bayesian analyses of randomized trials provide only probability
estimates for \emph{average} treatment effect and not for the elusive
\emph{individual} treatment effect.
